The symmetry problem of the \textit{Fermi} and eROSITA bubbles: A proof-of-concept study

### 2022-02-21 paper.tex
update

\begin{abstract}
A decade ago, the \textit{Fermi Gamma-Ray Space Telescope} reveals two large gamma-ray bubbles in the Galaxy,\
which extend nearly symmetrically $\sim50^{\circ}$ on either side of the Galactic disk.\
The recent discovery of eROSITA bubbles also shows a symmetrically enhanced X-ray\
emission from the shells around the eROSITA bubbles.\
To this end, previous simulation-based works assumed that the jets are vertical to the Galactic disk;\
however, there is a lack of preferred orientation of jets with respect to the Galactic disk.\
Using three-dimensional (3D) special relativistic hydrodynamic simulations that\
include cosmic rays (CRs) and thermal gas, we show that a thin interstellar medium disk is an essential\
component for the symmetry Galactic bubbles.\
We also produce simulated gamma-ray and\
microwave spectra from the inverse Compton scattering and synchrotron,\
and compare them with the observed counterparts in order to verify\
the oblique jets model. We find that\
(1) The Galactic bubbles are nearly symmetric about the Galactic plane albeit\
the jet is at an angle $45^{\circ}$ with respect to the disc normal.\
(2) The randomness of clumpy disk has a insignificant impact on the overall dynamic of the Galactic bubbles.\
The ambient stratification facilitates the eROSITA bubbles elongation significantly.
The development of the reverse shocks (the innermost bubbles) are always associated with the dense disc.

\end{abstract}

>>>>

\begin{abstract}
A decade ago, the \textit{Fermi Gamma-Ray Space Telescope} reveals two large gamma-ray bubbles in the Galaxy,\
which extend nearly symmetrically $\sim50^{\circ}$ on either side of the Galactic disk.\
The recent discovery of eROSITA bubbles also shows a symmetrically enhanced X-ray\
emission from the shells around the eROSITA bubbles.\
To this end, previous simulation-based works assumed that the jets are vertical to the Galactic disk;\
however, there is a lack of preferred orientation of jets with respect to the Galactic disk.\
Using three-dimensional (3D) special relativistic hydrodynamic simulations that\
include cosmic rays (CRs) and thermal gas, we show that a thin interstellar medium disk is an essential\
component for the symmetry Galactic bubbles.\
We also produce simulated gamma-ray and\
microwave spectra from the inverse Compton scattering and synchrotron,\
and compare them with the observed counterparts in order to verify\
the oblique jets model. We find that\
(1) The simulated Galactic bubbles are nearly symmetric about the Galactic plane albeit\
the jet is at an angle $45^{\circ}$ with respect to the disc normal.\
(2) The edge of the eROSITA bubbles is a forward shock,\
originally driven by oblique bipolar jets emanating from the GC 12.39 million years ago,\
and significantly stretched by the stratified atmosphere afterwards.\
(3) Followed by the forward shock is a tangling contact discontinuity,\
which we interpret as the edge of the \textit{Fermi} bubbles.\
The nature of the \textit{Fermi} bubbles is essentially a turbulent and high-temperature ($\sim2$ keV)\
plasma in pressure balance with the external medium.
(4) According to the microwave and leptonic gamma-ray spectra, the best-fitting\
CRe power-law index is found to be 2.4.\
The broad agreement between simulated and observed multiwavelength features\
releases the caveat given by earlier simulation-based studies:\
the jets shall be vertical to the disc normal.
\end{abstract}
